Inferring neural networks from imaging using partial correlation and sample weighting

### 2014-05-20 article.tex
First solution paragraph

\title[Connectomics challenge]{Inferring Neural Networks from Imaging Using Partial Correlation and Sample Weighting.}

@@

>>>>

\title[Connectomics challenge]{Inferring neural networks from imaging using
                               partial correlation and sample weighting}

@@

% Solution
In this paper, we describe a simple and a theoretically grounded approach
based on partial correlation to infer the neural connectivity network.
This is also the winning method of the Connectomics challenge.
